\section*{Biographies}
\noindent
{\em Diomidis Spinellis} is an Associate Professor at the Department of Management Science and Technology at the Athens University of Economics and Business, 
Greece.  His research interests include software engineering tools, programming languages, and computer security.  He holds an MEng in Software Engineering 
and a PhD in Computer Science both from Imperial College (University of London, UK).  He has written more than 70  technical papers in the areas of 
software engineering, information security, and ubiquitous computing. 
His book {\em Code Reading: The Open Source Perspective}
received a ``Software Development Productivity Award'' in 2004.  He has contributed software to the BSD Unix distribution, the X Window System, 
and is the author of a number of open-source software packages, libraries, and tools.

{\em Dr. Spinellis} is a member of the ACM, the IEEE, the Greek Computer Society, the Technical Chamber of Greece, and a founding member of the Greek 
Internet User's Society.  He is a co-recipient of the Usenix Association 1993 Lifetime Achievement Award.
\\
\\
{\em Vassilios Karakoidas} is a PhD candidate in Athens University of Economics and Business at the Department of Management Science and 
Technology. He holds an BSc in Computer Science (University of Piraeus) and an MSc in Information Systems (Athens University of 
Economics and Business). He is former member of the Health Informatics laboratory at University of Piraeus. He is now a member of 
ELTRUN/SENSE and has been involved in various research projects. The most recent are GEMINI and PRAXIS. His research interests include
Software Engineering, Programming Languages, Operating Systems and Networking.
\\
\\
{\em Dr Damianos Chatziantoniou} is visiting Assistant Professor in Athens University of Economics and Business and scientific consultant to 
ELTRUN. He has received his B.Sc. in Applied Mathematics from the University of Athens in Greece and continued his studies in Computer 
Science at New York University (M.Sc., 1993) and Columbia University (Ph.D., 1997), working with Ken Ross on data warehousing and decision
support systems. During his studies he was teaching and consulting regularly. Since 1997, Damianos is an assistant professor at Stevens 
Institute of Technology, an adjunct professor at Columbia University and president and co-founder of Panakea Software Inc. Panakea owns 
patent-pending algorithms for OLAP applications and developed a state-of-the-art decision support querying tool. Reference sites include AT\&T, 
New York Hospital and Dun-Bradstreet. Damianos is collaborating with AT\&T Labs-Research, Columbia University Medical Informatics Center, and 
National Technical University of Athens. His interests lie in the areas of data warehousing, decision support systems, OLAP and data mining. 
He has published papers and journals in VLDB, ICDE, EDBT and elsewhere.

